Human Motion Interface for Video Game Control

### 2022-03-14 proposal/proposal.tex
minor edits, LGTM

\section{Problem Description}
The human-computer interface behind many modern video games, using either handheld 
joystick controllers or keyboard and mouse input, is an example
of a typical human input device for computers, monitors, televisions, etc. There are two 
major drawbacks to traditional human input systems that are often overlooked: the input needed 
to achieve a certain effect has little to no correspondence to a physically-intuitive set 
of motions, and more importantly, inputs are heavily dependent on the user's fine motor skills. 
Fine motor skills used to interact with modern technology are heavily affected by factors such 
as muscular coordination disorders and old age. Computer vision, particularly the processes 
of motion tracking and human pose estimation, may allow us to create human-computer interfaces 
that link effect to physically-intuitive human motion inputs with little dependence on 
fine motor ability. We propose a vision-based computer-input system that maps gestures and 
motion of the user's body into computer input. We propose a car-racing simulator as a test 
subject for our system, and aim to intuitively control the motion of a player's virtual car 
with human body motion as the only action. Such a system would be instrumental in improving 
the accessibility of modern technology, with implementations far beyond the scope of computer 
games.

@@

The area of Human Pose Estimation is widely studied. Robust, optimized solutions exist 
that can help us with this step. One popular solution is derived from \cite{8765346}, and 
open-source code for the so called openpose library shows promising results for real-time 
human body segmentation.

@@

\section{Timeline}
We adopt an eight-week timeline for the development and documentation of this project, outlined 
more specifically below:
\begin{itemize}
    \item Week 0: Configure openpose to identify feature points from front and/or side cameras.
    \item Week 1: Perform any necessary optimizations to run openpose with as low latency as possible.
    \item Week 2: Finalize the set of trackable and detectable gestures, and map each one to a particular keyboard mapping in a physically-intuitive way.
    \item Week 3-4: Implement a feature tracking system, and confirm that each gesture accurately corresponds to a specific function with sufficient accuracy.
    \item Week 5: Interface detections with video game.
    \item Week 6: Optimize vision video game interaction for low latency.
    \item Week 7: Write paper describing project methodology, and explore future works inspired by this project.
\end{itemize}

>>>>

\section{Problem Description}
The human-computer interface behind many modern video games, uses either handheld 
joystick controllers or keyboard and mouse input, which are examples
of typical human input device for computers, monitors, televisions, etc. There are two 
major drawbacks to traditional human input systems that are often overlooked: the input needed 
to achieve a certain effect has little to no correspondence to a physically-intuitive set 
of motions, and more importantly, inputs are heavily dependent on the user's fine motor skills. 
Fine motor skills used to interact with modern technology are heavily affected by factors such 
as muscular coordination disorders and old age. Computer vision, particularly the processes 
of motion tracking and human pose estimation, may allow us to create human-computer interfaces 
that link effect to physically-intuitive human motion inputs with little dependence on 
fine motor ability or additional physical input devices. We propose a vision-based computer-input system that maps gestures and 
motion of the user's body into computer input. We also propose a car-racing simulator as a test 
subject for our system, and aim to intuitively control the motion of a player's virtual car 
with human body motion as the only action. Such a system would be instrumental in improving 
the accessibility of modern technology, with implementations far beyond the scope of computer 
games.

@@

The area of Human Pose Estimation is widely studied. Robust, optimized solutions exist 
that can help us with this step. One popular solution is derived from \cite{8765346} which uses Part Affinity Fields (PAFs) to learn to assosciate body parts with individuals in the image, and 
open-source code for the so called openpose library shows promising results for real-time 
human body segmentation.

@@

\section{Timeline}
We adopt an eight-week timeline for the development and documentation of this project, outlined 
more specifically below:
\begin{itemize}
    \item Week 0: Configure openpose to identify feature points from front and/or side cameras.
    \item Week 1: Perform any necessary optimizations to run openpose with as low latency as possible.
    \item Week 2: Finalize the set of trackable and detectable gestures, and map each one to a particular keyboard mapping in a physically-intuitive way.
    \item Week 3-4: Implement a real-time feature tracking system, and confirm that each gesture accurately corresponds to a specific function with sufficient accuracy.
    \item Week 5: Interface detections with video game.
    \item Week 6: Optimize vision video game interaction for low latency.
    \item Week 7: Write paper describing project methodology, and explore future works inspired by this project.
\end{itemize}
